Population statistics of companions to APOGEE red clump stars

### 2017-02-28 paper/main.tex
abstract attempt

% define macros for text
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\sdssiii}{\project{\acronym{SDSS-III}}}
\newcommand{\thejoker}{\project{The~Joker}}
\newcommand{\DR}{\acronym{DR13}}

@@

\begin{abstract}
% Context
% Aims
% Methods
% Results
\end{abstract}

>>>>

% define macros for text
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\sdssiii}{\project{\acronym{SDSS-III}}}
\newcommand{\thejoker}{\project{The~Joker}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\DR}{\acronym{DR13}}
\newcommand{\RC}{\acronym{RC}}

@@

\begin{abstract}
% Context
Radial-velocity measurements can be used to find stellar, sub-stellar,
and planetary companions of stars.
In the \apogee\ survey, we have multi-epoch radial-velocity measurements
for many red-giant stars, including many red-clump (\RC) stars.
Spectral analysis of these stars can be used to deliver masses (with
XXX precision) and 20-ish chemical abundance measurements (with YYY
precision).
% Aims
Here we perform a search for secondary companions of [number] \RC\ stars.
Because the primary-star masses are known, the mass-function degeneracy
is broken and the secondary-companion $m\,\sin i$ values can be inferred.
Also, if the primary and companion are assumed to be co-eval, the
abundances of the \RC\ star can be assumed to represent accurately the
abundances of the secondary.
% Methods
We use a data-driven model (\thecannon) of stellar spectra to deliver
each \RC\ mass and chemical abundances, and a custom-built Monte Carlo
sampler (\thejoker) to deliver (often highly multi-modal) posterior
beliefs about companion $m\,\sin i$, period, and other orbital parameters.
Our sampler permits us to accurately sample even the badly behaved
posterior pdfs obtained when there are as few an NNN observation
epochs per star.
We put these posterior samples---made under an interim prior---into a
hierarchical inference to obtain individual-companion-marginalized
posterior beliefs about the properties of the full secondary-companion
distribution in mass and period.
% Results
We deliver a catalog of QQQ companions [that meet some criteria], and
posterior samplings for all [number] stars in the parent sample.
We find that the period and mass distributions [have some properties].
We look for trends with chemical abundances, and we find tentative evidence
for ZZZ and WWW.
\end{abstract}
